### 2015-05-25 docs/report/context.tex
fixes context benchmark image.

We created a benchmark to explore the difference between sending the context and chains to execute as part of the same message, and using two different messages. The code for the benchmark is in the following listing:
\bmcode{http://jsperf.com/additional-sendingdata-comparison/2}{../../spikes/6.1/sendingAdditionalsSeqVsPar/jspBenchmark.js}

The results for the benchmark are displayed in Figure~\ref{fig:context-send}.
\img{Comparing small context message passing}{../../spikes/6.1/sendingAdditionalsSeqVsPar/jspBenchmark-all-browsers}{fig:context-send}

>>>>

We created a benchmark to explore the difference between sending the context and chains to execute as part of the same message, and using two different messages. The code for the benchmark is in the following listing:
\bmcode{http://jsperf.com/additional-sendingdata-comparison/3}{../../spikes/6.1/sendingAdditionalsSeqVsPar/jspBenchmark.js}

The results for the benchmark are displayed in Figure~\ref{fig:context-send}.
\img{Comparing small context message passing}{../../spikes/6.1/sendingAdditionalsSeqVsPar/jspBenchmark}{fig:context-send}
